Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-08-11 analysis/paper/paper.Rmd

```{r chi square testing}
# prepare contingency table for chi sqaure
ornaments_shape_chi <-
  ornaments_period_clean %>% 
  group_by(period, Categories) %>% 
  tally() %>% 
  filter(!Categories %in% c("Unknown Metal", 
                            "Perforated plate", 
                            "Knited item",
                            "Hair pin",
                            "Bone Ornament",
                            "Metal Piece",
                            "Glass ring")) %>% 
  spread(Categories, n)

>>>>

```{r chi-square-testing}
# prepare contingency table for chi sqaure
ornaments_shape_chi <-
  ornaments_period_clean %>% 
  group_by(period, Categories) %>% 
  tally() %>% 
  filter(!Categories %in% c("Unknown Metal", 
                            "Perforated plate", 
                            "Knited item",
                            "Hair pin",
                            "Bone Ornament",
                            "Metal Piece",
                            "Glass ring")) %>% 
  spread(Categories, n)
